---
title: "Lab 00 - Hello IDS!"
author: "Tigershengsheng"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Tiger", "Harry", "member 2", 
           "member 3", "member 4"),
  github_username = c("Tigershengsheng", "HarryPeng725", "username 2", 
                      "username 3", "username 4"), 
  colour = c("green", "blue", "colour 2", 
             "colour 3", "colour 4"),
  hobby = c("basketball", "basketball", "hobby 2", 
            "hobby 3", "hobby 4"),
  favourite_number = c(6, 6, NA, NA, NA)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

This bar chart shows each team member’s favourite number. The x-axis lists their GitHub usernames, while the height of each bar represents their favourite number. Each bar is coloured according to that person’s favourite colour. At the moment, only Tiger (green, 6) and Harry (blue, 6) are shown, as the remaining team members have not yet entered their favourite numbers.

